Preprocessing

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

# Perform initial tests and fix issues

@@

## Journals

@@

## Articles

@@

```{r}
d_articles %>%
  filter(exclusion_primary != exclusion_secondary)
```

@@

```{r}
# we've already dealt with cases where the decision to exclude differs, so we're not looking only at cases where the decision to exclude matches, but the reason for exclusion differs
d_articles %>%
  filter(exclusion_primary == exclusion_secondary, 
         exclusion_reason_primary != exclusion_reason_secondary) %>%
  select(article_id, sample_id, exclusion_reason_primary, exclusion_reason_secondary)
```

@@

# Resolve coding disagreements in journals data

@@

Make a tibble containing only the final coding for journals.\

>>>>

# Perform initial tests and fix some issues

@@

## Journal data initial tests

@@

## Articles data initial tests

@@

```{r}
# NOT RUN — used to identify cases where primary and secondary coder disagreed on whether to exclude.
# d_articles %>%
#   filter(exclusion_primary != exclusion_secondary)
```

@@

```{r}
# we've already dealt with cases where the decision to exclude differs, so we're not looking only at cases where the decision to exclude matches, but the reason for exclusion differs
# d_articles %>% # NOT RUN
#   filter(exclusion_primary == exclusion_secondary, 
#          exclusion_reason_primary != exclusion_reason_secondary) %>%
#   select(article_id, sample_id, exclusion_reason_primary, exclusion_reason_secondary)
```

@@

# Journals data — Resolve coding disagreements

@@

Make a tibble containing only the final coding for journals.
